Hypertension and microbiome

### 2019-06-12 articletwo.Rmd
eval false block

```{r multi model}
abund.genus.systm <- pseq.genus %>%
    abundances(., transform = "compositional") %>%
    t %>%
    as.data.frame %>%
    tibble::rownames_to_column("id")

@@

df.genus.systm %>%
    mutate(diff = -0.75418 * Anaerotruncus + 0.89265 * Sutterella) %>%
    pull(diff) %>%
    summary

>>>>

```{r multi model, eval = FALSE, include = FALSE}
abund.genus.systm <- pseq.genus %>%
    abundances(., transform = "compositional") %>%
    t %>%
    as.data.frame %>%
    tibble::rownames_to_column("id")

@@

df.genus.systm %>%
    mutate(diff = -0.75418 * Anaerotruncus + 0.89265 * Sutterella) %>%
    pull(diff) %>%
    summary
```
